%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Cloud Architect} % Job title
    {Amazon Web Services (AWS)} % Organization
    {Singapore} % Location
    {Aug. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tasked to design and build real-world solutions for clients using AWS cloud services.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Platform Engineer, Relational Database System (RDS) Team} % Job title
    {Shopee} % Organization
    {Singapore} % Location
    {Jun. 2020 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed a distributed solution for performing physical backups and restores on RDS MySQL clusters using XtraBackup engine.
        Enhancements include parallelised operations, failover and rollback mechanisms, data compression and checksum verification.}
        \item {Implemented an S3 Server with MinIO and Docker for streaming and storing database backups remotely.}
        \item {Designed and implemented an API Gateway for managing and killing database connections to RDS MySQL clusters and instances.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Lead (2020), Software \& DevOps Engineer (2019)} % Job title
    {Computing for Voluntary Welfare Organisations (CVWO)} % Organization
    {Singapore} % Location
    {May. 2019 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of 8 developers to work on 2 projects in 2020 – Senior Activities Centre / Neighborhood Links (SACNL) and GIC Sparks.}
        \item {SACNL is a workflow management system used by 12 elderly care centres across Singapore to serve thousands of old folks everyday. We refactored the existing Ruby on Rails application into an API backend server and developed a new frontend in React-Redux.}
        \item {GIC Sparks is a progressive web app developed for the GIC Sparks \& Smiles Program. We made substantial improvements to the UX and implemented new features such as cohort registration, CSV imports/exports and PDF reports.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
  {Data Analyst} % Job title
  {Cancer Science Institute (CSI)} % Organization
  {Singapore} % Location
  {Jan. 2019 - May. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed extensible command line tools for working with NSCC supercomputers to extract meaningful results from terabytes of raw genomic data. Results were used to profile algorithms that identify cancer-causing mutations based on cost, speed and accuracy.}
    \end{cvitems}
  }
\end{cventries}
